---
title: "R Notebook"
output: html_notebook
---

```{r}
bank_input = "~/Documents/Personal/Data_Projects/ML/projects/bank_marketing/data/bank/bank-full.csv"
addl_input = "~/Documents/Personal/Data_Projects/ML/projects/bank_marketing/data/bank-additional/bank-additional-full.csv"
df = read.csv(bank_input,sep=";")

df$outcome = ifelse(df$y=='yes',1,0)
df = df[,!(names(df) %in% c('y'))]

```
The major difference between the two datasets is that the `bank-addtional` has some macro-economic indicators.

```{r}

mycolSums<-function(x){
  return(x/sum(x))
}

X_train = read.csv("~/Documents/Personal/Data_Projects/ML/projects/bank_marketing/data/bank/processed/X_train.txt",sep='\t',header=FALSE)
y_train = read.csv("~/Documents/Personal/Data_Projects/ML/projects/bank_marketing/data/bank/processed//y_train.txt",sep="\t",header=FALSE)
feature_names = read.csv("~/Documents/Personal/Data_Projects/ML/projects/bank_marketing/data/bank/processed/features.txt",sep='\t',header=FALSE)

df = X_train
names(df) = as.character(feature_names[,1])
df[,'outcome'] = y_train[,1]

for (col in c("job_","month_","marital_","poutcome_","default_",
              "loan_","education_","housing_","contact_")){
  d = df[,grep(col,names(df))]
  df = df[,!(names(df) %in% grep(col,names(df),value=T))]
  w = which(d==1,arr.ind = T)
  col_name = strsplit(col,'_')[[1]]
  df[,col_name] <-(names(d)[w[order(w[,1]),2]])
  df[,col_name] <- sapply(strsplit(df[,col_name],"_"), `[`, 2)
}

df$month = factor(df$month,levels=c("jan","feb","mar","apr","may","jun","jul","aug",
                                    "sep","oct","nov","dec"))

X_val = read.csv("~/Documents/Personal/Data_Projects/ML/projects/bank_marketing/data/bank/processed/X_val.txt",sep='\t',header=FALSE)
y_val = read.csv("~/Documents/Personal/Data_Projects/ML/projects/bank_marketing/data/bank/processed/y_val.txt",sep="\t",header=FALSE)

vdf = X_val
names(vdf) = as.character(feature_names[,1])
vdf[,'outcome'] = y_val[,1]

for (col in c("job_","month_","marital_","poutcome_","default_",
              "loan_","education_","housing_","contact_")){
  d = vdf[,grep(col,names(vdf))]
  vdf = vdf[,!(names(df) %in% grep(col,names(vdf),value=T))]
  w = which(d==1,arr.ind = T)
  col_name = strsplit(col,'_')[[1]]
  vdf[,col_name] <-(names(d)[w[order(w[,1]),2]])
  vdf[,col_name] <- sapply(strsplit(vdf[,col_name],"_"), `[`, 2)
}

```

```{R}
m = cv.glmnet(as.matrix(X_train),as.factor(y_train[,1]),family='binomial',type.measure = 'class')
summary(m)
```

```{R}
codf = data.frame(summary(m)$coef)
sigdf = codf[codf[,'Pr...z..'] <0.05,]
sigdf[order(sigdf$Estimate,decreasing = T),]
```
```{r}
vdf$yhat = ifelse(predict(m,as.matrix(X_val),type='response') > 0.5, 1, 0)
table(vdf$yhat,vdf$outcome)
```




```{r}
with(df,plot(factor(outcome) ~ factor(month)))
```

```{R}
t = table(df$month,df$outcome)
t/rowSums(t)
```

Way more likely to succeed in mar and dec

```{r}
with(df,plot(factor(job)~ factor(month)))
```
```{R}
apply(table(df$job,df$month),2,mycolSums)
```
There seems to be some variation here across the year in terms of job. Maybe try an interaction term

```{R}
with(df,plot(poutcome~job))
```
```{R}
issuc = ifelse(df$poutcome == 'success', 1, 0)
m = glm(issuc ~ job,data=df,family='binomial')
summary(m)
```
Maybe an interaction term there as well

What about marital?

```{r}
summary(glm(outcome~marital*job,data=df,family='binomial'))
```

I think I'll try an interaction term there as well.


## Try code with bayesian stuff

toy data
```{r}
x = rep(1:5,6)
y = rep(1:0,15)
seg = rep(1:5,6)
df = data.frame(x=x,y=y,seg=seg)

probabilize_high_card_cat(df,y,x)
```